Methods for Large Scale Learning to Rank

### 2014-03-11 report/Chapters/RelatedWork.tex
volgende stap backward search

A one-level forward and backward reference search is used to find relevant papers missed so far. To handle the large volume of studies involved in the backward and forward reference search, relevance of the studies will be evaluated solely on the title of the study.\\

>>>>

A one-level forward and backward reference search is used to find relevant papers missed so far. To handle the large volume of studies involved in the backward and forward reference search, relevance of the studies will be evaluated solely on the title of the study. Backward reference search resulted in 10 studies regarded as potentially relevant based on the title of which x where actually relevant.\\
